A meta-analysis of fungicide spray schedules to minimise yield loss from powdery mildew in Australian mungbean

### 2020-08-24 03_Preliminary_analysis.Rmd
Add descriptive statistics for average mungbean yield

The data explored in the `PM_MB_dat` data frame is a list of mean values from each treatment in each respective experiment.
These preliminary analyses will focus on the change in mungbean yields, which is attributable to the fungicide treatment. 
Later in this document we will also consider the impact of fungicide treatments on disease incidence/severity.
Mean powdery mildew severity was recorded at the end of each growing season.
Some experiments recorded disease severity throughout the season and these were summarised with AUDPC.
AUDPC for trials which only provided final powdery mildew severity were calculated using the record of 'first sign of disease' and final assessment.

>>>>

The data explored in the `PM_MB_dat` data frame is a list of mean values from each treatment in each respective experiment.
These preliminary analyses will describe the data and then investigate any change in mungbean yields which is attributable to the fungicide treatment. 
### Descriptive statistics
#### Spatio-temporal variation

Lets look at how many trials were undertaken each season

```{r FinalTrialsForInclusion}
tmp1 <- PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   distinct(trial_ref, location, year)%>%
   arrange(year)
   table(tmp1$year)
```

Also the location of the trials

```{r FinalTrialsForInclusion}
tmp2 <- PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   distinct(trial_ref, location, year)%>%
   arrange(year)
   table(tmp1$location)
```

#### Mean yield

What is the variation in yield over all the trials (including non-DMI fungicide trials) in the no spray control and fungicide treated plots.  
```{r ControlYield_AllTrials}
PM_MB_dat %>%
   filter(fungicide_ai == "control")%>%
   summarise(mean_yield = mean(grain_yield.t.ha.),
             minimum_yield = min(grain_yield.t.ha.),
             maximum_yield = max(grain_yield.t.ha.),
             yield_stdev = sd(grain_yield.t.ha.))

What is the yield variation in no spray control trials yield over only the DMI fungicide trials.  
```{r ControlYield_DMITrials}
DMITrials <- PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   distinct(trial_ref)%>%
   pull()

PM_MB_dat %>%
   filter(trial_ref %in% DMITrials)%>%
   filter(fungicide_ai == "control" )%>%
   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
             minimum_yield = min(grain_yield.t.ha.*1000),
             maximum_yield = max(grain_yield.t.ha.*1000),
             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))

Mean yields in DMI fungicide treated plots
```{r Yield_DMITrials}
PM_MB_dat %>%
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   summarise(mean_yield = mean(grain_yield.t.ha.*1000),
             minimum_yield = min(grain_yield.t.ha.*1000),
             maximum_yield = max(grain_yield.t.ha.*1000),
             yield_sterr = sd(grain_yield.t.ha.*1000)/(sqrt(length(grain_yield.t.ha.))))

Lets look at the yield gains in each trial compared to the no spray control, we will also calculate the proportional grain yield gains.

Lets show the yield gains in each trial as a table and plot
```{r YieldGain_table}
PM_MB_dat %>%
   filter(trial_ref %in% DMITrials)%>%  # selects only the trials with DMI fungicide treatments
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   group_by(trial_ref, location, year)%>%
   summarise(yield_gain_m = mean(yield_gain),
             yield_gain_se = sd(yield_gain, na.rm = T)/sqrt(n()),
             yg_n = n(),
             .groups = "drop")%>%
   arrange(yield_gain_m)
```

```{r YieldGain_plot}
PM_MB_dat %>%
   filter(trial_ref %in% DMITrials)%>%  
   filter(fungicide_ai == "tebuconazole" |
             fungicide_ai == "propiconazole")%>%
   group_by(trial_ref, location, year)%>%
   summarise(yield_gain_m = mean(yield_gain),
             yield_gain_se = sd(yield_gain, na.rm = T)/sqrt(n()),
             .groups = "drop")%>%
   mutate(trial = paste(location,year,sep = "\n"))%>%
   ggplot(aes(reorder(trial, yield_gain_m), yield_gain_m))+
   geom_bar(stat = "identity")+
   geom_errorbar(width = 0.3 ,aes(ymax = yield_gain_m + yield_gain_se, 
                     ymin = yield_gain_m - yield_gain_se))+
   theme(axis.text.x = element_text(angle = 90, hjust = 1))

```{r}
mpg %>%
   group_by(manufacturer,drv,cyl)%>%
   filter(n() >= 2)%>%
   summarise(mean_Sp = mean(cty),
             stdev_h = sd(cty),
             n_group = n())

data()

mpg

Later in this document we will also consider the impact of fungicide treatments on disease incidence/severity.
Mean powdery mildew severity was recorded at the end of each growing season.
Some experiments recorded disease severity throughout the season and these were summarised with AUDPC.
AUDPC for trials which only provided final powdery mildew severity were calculated using the record of 'first sign of disease' and final assessment.
